|

### 2021-11-23 03-Chp-Systematic-Review-Methods.Rmd
Working version after Chapter 7

<!----------------------------------------------------------------------------->
(ref:lipidFractionsAD-cap) Random-effects meta-analysis of four lipid fractions (total cholesteol, HDL, LDL, and triglycerides) on Alzheimer's disease risk, standardised per 1-SD increase in the lipid fraction.

@@

>>>>

<!-- TODO This should also show Raffatin! -->

<!----------------------------------------------------------------------------->
(ref:lipidFractionsAD-cap) Random-effects meta-analysis of LDL on vascular dementia risk, standardised per 1-SD increase in the lipid fraction.

@@

<!-- TODO This is not technically - more studies available on vascular dementia -->

### 2021-11-23 06-Chp-IPD-Analysis.Rmd
Working version after Chapter 7

In order to investigate the interaction of patient-level characteristics (age and sex) with lipid levels, interaction terms for lipid-covariate terms were extracted and synthesised using a random effects meta-analysis. To avoid ecological bias, where the between-study association does not reflect the within-study associations, cohorts where there was no within-study variation in the covariate of interest were excluded from the interaction analysis for that covariate.[@burke2017] As an example, it is impossible to estimate the impact of sex on the lipid~dementia relationship in a study which contains female participants. All interaction analysis were performed using the common-set-adjusted model (Model 1).

>>>>

In order to investigate the interaction of patient-level characteristics (age and sex) with lipid levels, interaction terms for lipid-covariate terms were extracted and synthesised using a random effects meta-analysis.[@fisher2017a] To avoid ecological bias, where the between-study association does not reflect the within-study associations, cohorts where there was no within-study variation in the covariate of interest were excluded from the interaction analysis for that covariate.[@burke2017] As an example, it is impossible to estimate the impact of sex on the lipid~dementia relationship in a study which contains female participants. All interaction analysis were performed using the common-set-adjusted model (Model 1).

<!-- QUESTION Why was Ancelin, which provides summary level data stratified by sex, not included in the analysis? Several reasons: i) cause it was not adjusted for the same covariates; ii) because the -->
